
% FIXME Does this belong in the lit review?
\section{Methods for Sampling Web Data}
I intend to cover methods people use for sampling.  This will include all the various tools (and commentary on each, though there will likely not be time for an evaluation of each).  From this, various deficiencies will be extracted, which will form the basis for my improved tools.

\subsection{Review of Current Use}
\todo[color=blue!20, noline]{WHEN}
Here I'll discuss current usage of WaC work, and focus on why attrition is likely to be important to CL in general.  This will serve part of the rationale of this chapter.

\subsection{Evaluation of Methodologies}
Hetre I'll cover the various tools and comment on each.  This will form motivation for the lower sections, justifying choices below.



% --------------- %
\section{Re-Implementation of Sharoff's Paper}
\todo[color=blue!20, noline]{WHEN + WHERE}
This will form, basically, a motivating example for the incomparability of results taken years apart from the web.



\section{Comprehensive DA Study}
\todo[color=blue!20, noline]{WHEN}
The content from my longitudinal study will fall here, though it's possible to populate some of this will LREC and other work.

\subsection{Method}
In addition to a discussion of best practice (perhaps best moved elsewhere?), outline the study:
\begin{itemize}
	\item The process of sampling, related to the lit review;
	\item The choice of input data.
\end{itemize}


\subsection{Evaluation \& Analysis}
\todo[color=blue!20, noline]{WHEN}
Analyse the results, and provide an evaluation of:
\begin{itemize}
	\item The study itself, and the quality of its findings;
	\item The impact any identified effects are likely to have upon data integrity.
\end{itemize}


